Compare with SH HA paper

### 2017-01-19 Code/Run_model_on_SH_data/Prep SH HA data for our analysis.Rmd
added Alabama tests

prop.table(table(is.na(dtotal$Count[dtotal$State2 == "New York"])))
prop.table(table(is.na(dtotal$Count[dtotal$State2 == "Georgia"])))
prop.table(table(is.na(dtotal$Count[dtotal$State2 == "Florida"])))

@@

test.le.fx(dtotal, "New York", "Male", "White", 1990)
test.le.fx(dtotal, "New York", "Male", "White", 2009)
```

>>>>

prop.table(table(is.na(dtotal$Count[dtotal$State2 == "New York"])))
prop.table(table(is.na(dtotal$Count[dtotal$State2 == "Georgia"])))
prop.table(table(is.na(dtotal$Count[dtotal$State2 == "Florida"])))
table(is.na(dtotal$Count[dtotal$State2 == "Alabama" & dtotal$Year3 == 1990]))

@@

test.le.fx(dtotal, "New York", "Male", "White", 1990)
test.le.fx(dtotal, "New York", "Male", "White", 2009)

test.le.fx(dtotal, "Alabama", "Male", "White", 1990)
test.le.fx(dtotal, "Alabama", "Male", "White", 2009)

test.le.fx(dtotal, "Alabama", "Male", "Black", 1990)
#test.le.fx(dtotal, "Alabama", "Male", "Black", 2009)

```
